### 2016-10-03 Paper_v7.tex
DB edits 3

\subsection*{Identification of a novel LEF-1 regulator}
During model identification, we found that consistent TGF-$\beta$ induced EMT required an additional regulatory protein.
This protein, which we called hypothetical regulator 1 (YREG1), was required to mediate between SNAIL/SLUG transcriptional activity
and the upregulation of LEF-1 expression following TGF-$\beta$1/2 exposure.
SNAIL/SLUG are well known transcriptional repressors \citep{Hemavathy:2000aa,Hemavathy:2000ab,Dhasarathy:2011aa}, although there are a few studies
which suggest that at least SNAIL can also act as a transcriptional activator \citep{Guaita:2002aa}.
In the model, we assumed the expression of SNAIL/SLUG was likely regulated by AP1/SP1 \citep{Jackstadt:2013aa}.
Thus, upon receiving a TGF-$\beta$1/2 signal, the model predicted enhanced SNAIL/SLUG expression, consistent with experimental observations.
TGF-$\beta$1/2 stimulation also induces LEF-1 expression. However, literature evidence suggested that LEF-1 expression was not strongly dependent upon AP1/SP1 activity \citep{Eastman:1999aa}.
Thus, either SNAIL/SLUG are acting as inducers (contrary to substantial biochemical evidence) or, they are repressing the expression of an intermediate repressor.
Given the biochemical evidence supporting SNAIL/SLUG as repressors, we created YREG1 a hypothetical intermediate repressor whose
expression is downregulated by SNAIL/SLUG. The literature data therefore suggested that YREG1 had two transcriptional targets, LEF-1 and TGF-$\beta$3.
By adding this regulator, our simulations became consistent with training and literature data.
Medici et al. suggested that feedback between $\beta$-catenin and LEF-1 was likely, although this feedback had yet to be identified \citep{Medici:2008fk}.
Low levels of YREG1 expression were present in all simulations to regulate the formation of the $\beta$-catenin-LEF-1 complex.
To test the potency of YREG1, we conducted over-expression and knockdown simulations following the addition of TGF-$\beta$1/2 (Fig. \ref{fg:F4}C and \ref{fg:F4}D).

% TODO: REVISE -----
% In the absence of YREG1, most of the population failed to consistently respond to TGF-$\beta$1/2 exposure compared to the wild-type (Fig. \ref{fig:S8}A).
% Conversely, YREG1 overexpression revealed an exclusively epithelial phenotype following TGF-$\beta$1/2 stimulation (Fig. \ref{fig:S8}B).]
% Overexpression of YREG1 repressed LEF-1 and TGF-$\beta$3 expression,
% thereby not allowing free $\beta$-catenin to form the $\beta$-catenin-LEF-1 complex which promotes mesenchymal gene expression, or SMAD activity following from autocrine TGF-$\beta$3 signaling.
% Taken together, we found that low YREG1 expression was necessary for stabilizing EMT,
% while elevated YREG1 levels limited the extent of EMT induction.

@@

% ####Analysis of the connectivity and information flow through the signaling architecture suggested that Sp1 and NFAT action could be manipulated \emph{independently} by simultaneous TGF$-\beta$1/2 and VEGF-A stimulation (Fig. \ref{fg:S1}).

@@

Sequential activation of MAPK and Smad pathways were initiated upon addition of TGF$-\beta$1/2.  Briefly, TGF$-\beta$2 signals through the RAS-RAF-MEK-ERK pathway to up-regulate Snail and Slug expression \citep{Medici:2006qa}.  Snail, a known repressor of junctional proteins, inhibits the expression of E-cadherin \citep{Cano:2000kh}. This initial repression of E-cadherin leads to a release of $\beta$-catenin from the cell membrane. Cystolic $\beta$-catenin can then translocate to the nucleus and form transcriptional complexes with TCF-4 to drive TGF$-\beta$3 expression \citep{Medici:2008fk}. TGF$-\beta$3 signals to the cells interior by binding to type II receptors, which form heterodimers with type I receptors (ALK5) \citep{Derynck:2003fc}. This activates the receptors serine/threonine kinase activity to phosphorylate and activate the receptor Smads 2/3 \citep{Massague:2005qc}.

@@

\citep{Zhou:2004kx,Larue:2005vn}.
VEGF-A activation of NFATc1 takes place through calcineurin signaling leading to an enhancement of E-cadherin expression \citep{Suehiro:2014aa},

@@

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/Fig4_mechanism.pdf}
\caption{Analysis of underlying signaling responses.
(A) We examined the distribution of NFATc1 and AP1/SP1 in cells containing the hybrid phenotype (VEGF-A + TGF$-\beta$2 case), showing the potential for cells to express both SP1 and NFATc1 in a non exclusive manner.
(B) We were able to show a fit to an additional objective demonstrating the actiation of GSK3 through PI3K. Our model captures this activation through TGF$-\beta$3 signaling. LY294002 is a PI3K inhibitor.
(C) We identified a novel regulator of LEF1 called YREG1 that allows Snail/Slug to emulate an inducer by repressing YREG1. Over expression of YREG1 increases the degree of E-cadherin expression, stabalizing the epithelial phenotype.
(D) Kockout of YREG1 leads to a loss of both E-cadherin and vimentin for cells that were inherently activated in the untreated population.}\label{fg:F4}
\end{figure}

>>>>

\subsection*{Identification of a novel LEF-1 regulator}
During model identification, we found that consistent TGF-$\beta$ induced EMT from a stable epithelial cell population required an additional regulatory protein.
This protein, which we called hypothetical regulator 1 (YREG1), was required to mediate between SNAIL/SLUG transcriptional activity
and the upregulation of LEF-1 expression following TGF-$\beta$1/2 exposure.
SNAIL/SLUG are well known transcriptional repressors \citep{Hemavathy:2000aa,Hemavathy:2000ab,Dhasarathy:2011aa}, although there are a few studies
which suggest that at least SNAIL can also act as a transcriptional activator \citep{Guaita:2002aa}.
In the model, we assumed the expression of SNAIL/SLUG was likely regulated by AP1/SP1 \citep{Jackstadt:2013aa}.
Thus, upon receiving direct Snail/Slug and TGF-$\beta$3 signals, the model predicted enhanced SNAIL/SLUG expression, consistent with experimental observations.
TGF-$\beta$1/2 stimulation also induces LEF-1 expression. However, literature evidence suggested that LEF-1 expression was not strongly dependent upon AP1/SP1 activity \citep{Eastman:1999aa}.
Thus, either SNAIL/SLUG are acting as inducers (contrary to substantial biochemical evidence) or, they are repressing the expression of an intermediate repressor.
Given the biochemical evidence supporting SNAIL/SLUG as repressors, we created YREG1 a hypothetical intermediate repressor whose
expression is downregulated by SNAIL/SLUG. The literature data therefore suggested that YREG1 had two transcriptional targets, LEF-1 and TGF-$\beta$3.
By adding this regulator, our simulations became consistent with training and literature data.
Medici et al. suggested that feedback between $\beta$-catenin and LEF-1 was likely, although this feedback had yet to be identified \citep{Medici:2008fk}.
Low levels of YREG1 expression were present in all simulations to regulate the formation of the $\beta$-catenin-LEF-1 complex.
To test the effect of YREG1 on the epithelial population, we conducted over-expression and knockdown simulations on untreated cells (Fig. \ref{fg:F4}C and \ref{fg:F4}D).
In the absence of YREG1, most of the population failed to consistently to retain a stable epithelial state (Fig. \ref{fig:F4}D).
Conversely, YREG1 overexpression revealed an enhanced epithelial phenotype, while some inherently transformed cells moved towards a hybrid phenotype  (Fig. \ref{fig:F4}C).
Elevation of YREG1 repressed LEF-1 and TGF-$\beta$3 expression, thereby not allowing free $\beta$-catenin to form the $\beta$-catenin-LEF-1 complex which promotes mesenchymal gene expression, or SMAD activity following from autocrine TGF-$\beta$3 signaling. Taken together, we found that low YREG1 expression was necessary for producing a stabile the model with an epithelial phentoype that is inducable across multiple stimuli such as TGF-$\beta$1/2, TGF-$\beta$3 and SNAIl/SLUG transfection, as seen in the training objectives.

@@

@@

Sequential activation of MAPK and Smad pathways were initiated upon addition of TGF$-\beta$1/2.  Briefly, TGF$-\beta$2 signals through the RAS-RAF-MEK-ERK pathway to up-regulate Snail and Slug expression \citep{Medici:2006qa}.  Snail, a known repressor of junctional proteins, inhibits the expression of E-cadherin \citep{Cano:2000kh}. This initial repression of E-cadherin leads to a release of $\beta$-catenin from the cell membrane. This release of $\beta$-catenin can then translocate to the nucleus and form transcriptional complexes with TCF-4 to drive TGF$-\beta$3 expression \citep{Medici:2008fk}. The PI3K to GSK3 pathway was included and acted as an activating mechanism of $\beta$-catenin signaling through TGF$-\beta$3 signaling \c\
itep{Medici:2008fk}. GSK3 is known to act on $\beta$-catenin signaling through the ubiquitin-proteasome pathway
\citep{Zhou:2004kx,Larue:2005vn}. Thereby, further $\beta$-catenin release also resulted from by TGF$-\beta$3 signals to the cells interior by binding to type II receptors, which form heterodimers with type I receptors (ALK5) \citep{Derynck:2003fc}. This activates the receptors serine/threonine kinase activity to phosphorylate and activate the receptor Smads 2/3 \citep{Massague:2005qc}. In the model, receptors are represented as either bound or unbound complexes. 

@@

\citep{Zhou:2004kx,Larue:2005vn}. Lastly, VEGF-A activation of NFATc1 takes place through calcineurin signaling leading to an enhancement of E-cadherin expression \citep{Suehiro:2014aa},

@@

\begin{figurey}
\includegraphics [width=1.0\linewidth] {./figs/Fig4_mechanism.pdf}
\caption{Analysis of underlying signaling responses.
(A) We examined the distribution of NFATc1 and AP1/SP1 in cells containing the hybrid phenotype (VEGF-A + TGF$-\beta$2 case), showing the potential for cells to express both SP1 and NFATc1 in a non exclusive manner.
(B) We were able to show a fit to an additional objective demonstrating the actiation of GSK3 through PI3K. Our model captures this activation through TGF$-\beta$3 signaling. LY294002 is a PI3K inhibitor.
(C) We identified a novel regulator of LEF1 called YREG1 that allows Snail/Slug to emulate an inducer by repressing YREG1, which was required to stabalize the untreated population. 
YREG1 overexpression revealed an enhanced epithelial phenotype, while some inherently transformed cells moved towards a hybrid phenotype.
(D) In the absence of YREG1, most of the population failed to consistently to retain a stable epithelial state.}\label{fg:F4}
\end{figure}
